\Large \bf GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers

### 2015-04-15 doc/report/Final/usenix.tex
final report double column format

%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst, 
%  which replaces the standard style unstr.bst.

%%\documentclass[]{spie}  %>>> use for US letter paper
\documentclass[a4papert,12pt]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX 
%  installations. 
\usepackage[]{graphicx}
\usepackage[sort, numbers]{natbib}
\usepackage{hyperref}
\usepackage{adjustbox,lipsum}
\graphicspath{ {/Users/anirudhnair/code/GeoSched/src/GoogleTrace/plots} }
\usepackage{subfig}
\usepackage[margin=0.6in]{geometry}

\title{GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers} 
%\author{Anirudh Jayakumar and Harshit Dokania \\
%University of Illinois at Urbana-Champaign 
%\{ajayaku2,hdokani2\}@illinois.edu 
%}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%>>>> uncomment following for page numbers
% \pagestyle{plain}    
%>>>> uncomment following to start page numbering at 301 
%\setcounter{page}{301}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
Today, many of the leading cloud service providers have geographically distributed data centers to serve millions of users around the world. The need for a geo-distributed data center arises from the need to provide low-latency and  high-availability of the different services. The workloads that run on these data centers are also highly diverse. A typical data centers run jobs of different kinds including business-critical workloads---web servers, mail servers, instant messaging services etc, big-data processing, real-time data analytics and HPC jobs. As cloud services grow to serve more customers, there is an increasing need for a workload provisioning mechanism which can minimize the cost of operation of the data center while minimizing SLA violations and also minimizing the user-perceived latency.

We present GeoSched, a job provisioning framework that is workload aware, energy-aware and cooling-aware. GeoSched considers the workload type (batch process, real-time processing, web-service), the energy source of the data center (brown and green energy), electricity pricing of the region and cooling techniques used in the data center (air economizer). We GeoSched on industry workload traces and also on synthetic workloads that can mimic the real-world data center workload. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
\label{sec:intro}  % \label{} allows reference to this section
Cost minimization has been extensively studied both in the context of a single data center and a geo-distributed data center. Most of the work has been targeted towards minimizing the energy consumption of the data center to reduce the operational cost. For example, the work by Gu et al. \cite{gu2014cost} studies the influence of task assignment, data placement  and data movement on the operational expenditure of large-scale geo-distributed data centers for big data applications. The authors jointly optimize  these three factors by proposing a 2-D Markov chain to derive the average task completion time and solve the model as a MILP problem. On similar lines Agarwal et al. \cite{agarwal2010volley} propose an automated data placement mechanism Volley for geo-distributed cloud services with the consideration of WAN bandwidth cost, data center capacity limits, data inter-dependencies, etc.

@@

There are also research done to look at the impact of failures in data centers on the operational cost. The work by Cui et al. \cite{cui2014shadows} considers the increase in energy consumption due to failures in large scale clouds. A slower shadow replication of the main process is used to recover from faults thereby saving energy upto 30\%. Guenter et al. \cite{guenter2011managing} also considers different trade-offs between cost, performance and reliability to formulate an optimization problem that minimizes energy costs, reliability costs and unmet demands. VM migration techniques are also used extensively to increase the energy efficiency of cloud data centers. One such approach is proposed by Rodero et al. \cite{rodero2012energy} where the author  propose to use applications۪s profiling (CPU, memory, bandwidth) to  design application-centric energy-aware strategy for VM allocation during VM migration.

Researchers have also studied the efficient use of green energy in data centers. Goiri et al. \cite{goiri2011greenslot} propose a system GreenSlot that maximizes the use of green energy available at data centers while ensuring all job deadlines are met. GreenSlot predicts the solar energy available in data centers in near future and schedules the workload to maximize green energy consumption and meeting jobs۪s deadlines. Green- Slot can increase green energy consumption by up to 117\% and decrease energy cost by up to 39\%, compared to a conventional scheduler.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Statement}

Minimize the total cost of operations of a geo-distributed data center running cloud workloads by minimizing the energy costs subject to business constraints like the service level agreement(SLA) and other technical constraints like data center capacity limits. The energy costs will depend on the power usage of the IT infrastructure and also the energy required by the cooling infrastructure to maintain the desired temperature inside the data center. Additionally, the solution should also consider the different energy source(green and brown) available at the data center and the different workload types that are typical to a cloud data center.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

\section{Cloud Workload } 
With the increase in the adoption of cloud computing by businesses around the world, more and more workloads are moving out of traditional data centers into the cloud. A cloud data center typically handles a range of IT workloads. These workloads include service-critical and latency sensitive interactive applications that run 24x7 such as instant messengers, e-mail applications and other internet services, and batch-style applications such as scientific HPC applications, BigData applications like financial analysis and MapReduce applications. A thoughtful management of these workloads are necessary not only to provide customers with low-latency services but also to reduce the energy consumption of the data centers that run these workloads. A good way to study these workloads are by analyzing real-world or synthetic workload traces. We look at cloud workload traces in detail in section \ref{traces} and \ref{googletrace}

@@

\begin {table}[ht]
\centering
 \scalebox{0.9}{\begin{tabular}{ | p{4cm} |l  |p{11 cm}|  }
    \hline
    \bf{Field Name} & \bf{Type} & \bf{Description}   \\ \hline
     JobID & INTEGER  & Unique job identifier for each job\\ \hline
     Arrival Time & INTEGER & Arrival time in microseconds \\ \hline
     Scheduled Time & INTEGER  & Arrival time in microseconds\\ \hline
     Finish Time & INTEGER  & Arrival time in microseconds\\ \hline
     Schedule class & INTEGER  & Latency class of the job. \\ \hline
     Tasks & INTEGER  & Total number of tasks in the job. \\ \hline
     Total CPU& INTEGER  & Aggregate sum of CPU used by all the tasks in the job\\ \hline
     Total Memory& INTEGER   & Aggregate sum of memory used by all the tasks in the job \\ \hline
     User& INTEGER  & Unique user identifier \\ \hline
     SLA Param1&  FLOAT & SLA parameter placeholder\\ \hline
     SLA Param2&  FLOAT & SLA parameter placeholder\\ \hline
     SLA Param3&  FLOAT & SLA parameter placeholder\\ \hline
    \end{tabular}}
    \caption {Trace format description} \label{tab:format} 
\end{table}

@@

\begin{figure}[ht] 
\centering
\includegraphics[scale=0.40]{arrivalrate.png}
\caption{Arrival rate of jobs }
\label{fig:arrivalrate}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[scale=0.65]{pie}
\caption{ Distribution of job count in various schedule classes}
 \label{fig:pie}
\end{figure}

\begin{table}
\adjustbox{max width=1\textwidth}{

\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
\hline
 & \multicolumn{3}{l|}{\bf{Trace A}} & \multicolumn{3}{l|}{\bf{Trace B}} & \multicolumn{3}{l|}{\bf{Trace C}} & \multicolumn{3}{l|}{\bf{Trace D}} & \multicolumn{3}{l|}{\bf{Trace E}} \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}Sched\\ Class\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg \\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} \\ \hline
0 & 0.075 & 0.051 & 415 & 0.123 & 0.096 & 345 & 0.083 & 0.065 & 385 & 0.093 & 0.092 & 373 & 0.093 & 0.074 & 333 \\ \hline
1 & 0.087 & 0.029 & 729 & 0.086 & 0.032 & 760 & 0.082 & 0.028 & 711 & 0.073 & 0.030 & 743 & 0.093 & 0.043 & 693 \\ \hline
2 & 0.067 & 0.043 & 1028 & 0.096 & 0.058 & 872 & 0.088 & 0.057 & 918 & 0.073 & 0.045 & 707 & 0.084 & 0.049 & 832 \\ \hline
3 & 0.088 & 0.12 & 1105 & 0.099 & 0.12 & 82 & 0.101 & 0.012 & 7961 & 0.081 & 0.051 & 17135 & 0.089 & 0.061 & 9021 \\ \hline
\end{tabular}
}
\caption {Trace set statistics} \label{tab:tracestat} 
\end{table}

@@

\begin{figure}[] 
\centering
\includegraphics[scale=0.40]{runtime}
\caption{CDF of the job duration}
\label{fig:runtime}
\end{figure}

@@

\begin{figure} %
    \centering
    \subfloat[CPU resource ]{{\includegraphics[width=9cm]{cpu} }}%
    \subfloat[RAM resource]{{\includegraphics[width=9cm]{mem} }}%
    \caption{CDF of resource requested by jobs}%
    \label{fig:resource}%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Center Profiling } \label{sec:datacenter}
In order to run our experiments, we need to collect information about data centers that will help us make better scheduling decisions. We call this process data center profiling. The major energy costs in data center are from running the IT resources and from cooling the data centers. We create a profile for each of the data center with the information that effects the energy costs.

\begin{table}[h] 
 \centering
\begin{tabular}{|l|l|l|}
\hline
\bf{Location}                        & \bf{Label} & \bf{Associated Trace} \\ \hline
Berkeley County, South Carolina & DC1   & A                \\ \hline
Lenoir, North Carolina          & DC2   & B                \\ \hline
Singapore                       & DC3   & C                \\ \hline
Quilicura, Chile                & DC4   & D                \\ \hline
Dublin, Ireland                 & DC5   &   E               \\ \hline
\end{tabular}
\caption {Data center location information} \label{tab:dc}
\end{table}

@@

\begin{table}[h] 
 \centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf{Node count}      &       \bf{Architecture}          & \bf{CPU} & \bf{Memory} \\ \hline
6732 & B & 0.5 & 0.50   \\ \hline
3863 & B & 0.5 & 0.25   \\ \hline
1001 & B & 0.5 & 0.75   \\ \hline
795 & C & 1 & 1   \\ \hline
126 & A & 0.25 & 0.25   \\ \hline
52 & B & 0.5 & 0.12  \\ \hline
5 & B & 0.5 & 0.3  \\ \hline
5 & B & 0.5 & 0.97  \\ \hline
3 & C & 1 & 0.50  \\ \hline
1 & B & 0.5 & 0.06  \\ \hline
\end{tabular}
\caption {Data center IT resource configuration} \label{tab:dcres}
\end{table}

@@

\begin{figure} %
    \centering
    \subfloat[Daily Average Temperature ]{{\includegraphics[width=9cm]{AverageTemp} }}%
    \subfloat[Daily Maximum Variation]{{\includegraphics[width=9cm]{Variation} }}%
    \caption{Temperature variation for the year 2013}%
    \label{fig:temp}%
\end{figure}

@@

\section{Scheduler simulator} 
We plan to implement our simulator using CloudSim \cite{calheiros2011cloudsim}. CloudSim is an extensible simulation toolkit that enables modeling and simulation of Cloud computing systems and application provisioning environments. The CloudSim toolkit supports both system and behavior modeling of Cloud system components such as data centers, virtual machines (VMs) and resource provisioning policies.
\subsection{Components}
\begin{list2} %Job Description%
\item \textbf{Datacenter:} This component will simulate a data center. This composed of 1) scheduler that implements a specific provisioning algorithm, 2) data center profile database, 3) a work trace reader and 4)proxy elements of other data center for inter-data center communication\
\item \textbf{DataCenter Proxy}: All interactions with the data center will be through a proxy. Each datacenter will hold the proxies to other data centers.\
\item \textbf{Scheduler:} This component will implement the optimization technique and schedule jobs onto data centers.\
\item \textbf{Datacenter Profile DB}: This components contains the temperature and electricity data. Scheduler will access this to make provisioning decisions.\
\end{list2}

\begin{figure}[] 
\centering
\includegraphics[scale=0.60]{component}
\caption{Simulation components and their interaction}
\label{fig:component}
\end{figure}

@@

\section{Conclusion}
We have completed the work trace analysis and data center profiling parts of the project. Currently the simulator is being implemented, following which we will work on the energy minimization techniques and the final evaluation of these techniques. If time permits, we would also like to consider green energy in our provisioning mechanism. Section \ref{sec:mile} shows the current state sand future directions of the project. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\section{Scheduling Algorithm}

@@

\section{ Milestones} \label{sec:mile}
\adjustbox{max width=1\textwidth}{
    \begin{tabular}{ | p{4cm} |l  |p{11 cm}| l |  }
    \hline
    \bf{Item} & \bf{Deadline} & \bf{Description}  &  \bf{Status} \\ \hline
    Study real-world and synthetic workloads & 10\textsuperscript{th} March  & We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011. & Completed  \\ \hline
    Data Center profile & 20\textsuperscript{th} March  & In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-distributed data centers. & Completed\\ \hline
    Simulator design and implementation& 12\textsuperscript{th} April  & Implement the simulator infrastructure for multi-datacenter environment.  & In progress \\ \hline
    Feature Extraction and Optimization & 25\textsuperscript{th} April  & Here we identifying all the necessary features that contribute to the energy cost  and build an optimization technique which is adaptive to workload characteristics and data center's resource capacity and electricity costs & TBD \\ \hline
    Evaluation & 7\textsuperscript{th} May  & This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above & TBD \\ \hline

    \end{tabular}
}

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

>>>>

% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file.

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage[]{graphicx}
\usepackage[sort, numbers]{natbib}
\usepackage{hyperref}
\usepackage{adjustbox,lipsum}
\usepackage{subfig}

\title{\Large \bf GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers} 
\author{
{\rm Anirudh Jayakumar}
\hspace{20 mm}
{\rm Harshit Dokania}\\
University of Illinois at Urbana-Champaign
}

@@

@@

\subsection*{ABSTRACT}
Today, many of the leading cloud service providers have geographically distributed data centers to serve millions of users around the world. The need for a geo-distributed data center arises from the need to provide low-latency and  high-availability of the different services. The workloads that run on these data centers are also highly diverse. A typical data centers run jobs of different kinds including business-critical workloads---web servers, mail servers, instant messaging services etc, big-data processing, real-time data analytics and HPC jobs. As cloud services grow to serve more customers, there is an increasing need for a workload provisioning mechanism which can minimize the cost of operation of the data center while minimizing SLA violations and also minimizing the user-perceived latency.

We present GeoSched, a job provisioning framework that is workload aware, energy-aware and cooling-aware. GeoSched considers the workload type (batch process, real-time processing, web-service), the energy source of the data center (brown and green energy), electricity pricing of the region and cooling techniques used in the data center (air economizer). We GeoSched on industry workload traces and also on synthetic workloads that can mimic the real-world data center workload.

\section{INTRODUCTION}
\label{sec:intro}

\textbf{Problem Statement:} Minimize the total cost of operations of a geo-distributed data center running cloud workloads by minimizing the energy costs subject to business constraints like the service level agreement(SLA) and other technical constraints like data center capacity limits. The energy costs will depend on the power usage of the IT infrastructure and also the energy required by the cooling infrastructure to maintain the desired temperature inside the data center. Additionally, the solution should also consider the different energy source(green and brown) available at the data center and the different workload types that are typical to a cloud data center.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{RELATED WORK}
\label{sec:related} 
Cost minimization has been extensively studied both in the context of a single data center and a geo-distributed data center. Most of the work has been targeted towards minimizing the energy consumption of the data center to reduce the operational cost. For example, the work by Gu et al. \cite{gu2014cost} studies the influence of task assignment, data placement  and data movement on the operational expenditure of large-scale geo-distributed data centers for big data applications. The authors jointly optimize  these three factors by proposing a 2-D Markov chain to derive the average task completion time and solve the model as a MILP problem. On similar lines Agarwal et al. \cite{agarwal2010volley} propose an automated data placement mechanism Volley for geo-distributed cloud services with the consideration of WAN bandwidth cost, data center capacity limits, data inter-dependencies, etc.

@@

There are also research done to look at the impact of failures in data centers on the operational cost. The work by Cui et al. \cite{cui2014shadows} considers the increase in energy consumption due to failures in large scale clouds. A slower shadow replication of the main process is used to recover from faults thereby saving energy upto 30\%. Guenter et al. \cite{guenter2011managing} also considers different trade-offs between cost, performance and reliability to formulate an optimization problem that minimizes energy costs, reliability costs and unmet demands. VM migration techniques are also used extensively to increase the energy efficiency of cloud data centers. One such approach is proposed by Rodero et al. \cite{rodero2012energy} where the author  propose to use applicationss profiling (CPU, memory, bandwidth) to  design application-centric energy-aware strategy for VM allocation during VM migration.

Researchers have also studied the efficient use of green energy in data centers. Goiri et al. \cite{goiri2011greenslot} propose a system GreenSlot that maximizes the use of green energy available at data centers while ensuring all job deadlines are met. GreenSlot predicts the solar energy available in data centers in near future and schedules the workload to maximize green energy consumption and meeting jobss deadlines. Green- Slot can increase green energy consumption by up to 117\% and decrease energy cost by up to 39\%, compared to a conventional scheduler.

\fi

\section{CLOUD WORKLOADS } 
With the increase in the adoption of cloud computing by businesses around the world, more and more workloads are moving out of traditional data centers into the cloud. A cloud data center typically handles a range of IT workloads. These workloads include service-critical and latency sensitive interactive applications that run 24x7 such as instant messengers, e-mail applications and other internet services, and batch-style applications such as scientific HPC applications, BigData applications like financial analysis and MapReduce applications. A thoughtful management of these workloads are necessary not only to provide customers with low-latency services but also to reduce the energy consumption of the data centers that run these workloads. A good way to study these workloads are by analyzing real-world or synthetic workload traces. We look at cloud workload traces in detail in section \ref{traces} and \ref{googletrace}

@@

\begin {table}[]
\centering
 \scalebox{0.7}{\begin{tabular}{ | p{3cm} |l  |p{6 cm}|  }
    \hline
    \bf{Field Name} & \bf{Type} & \bf{Description}   \\ \hline
     JobID & INT  & Unique job identifier for each job\\ \hline
     Arrival Time & INT & Arrival time in microseconds \\ \hline
     Scheduled Time & INT  & Arrival time in microseconds\\ \hline
     Finish Time & INT  & Arrival time in microseconds\\ \hline
     Schedule class & INT  & Latency class of the job. \\ \hline
     Tasks & INT  & Total number of tasks in the job. \\ \hline
     Total CPU& INT  & Aggregate sum of CPU used by all the tasks in the job\\ \hline
     Total Memory& INT   & Aggregate sum of memory used by all the tasks in the job \\ \hline
     User& INT  & Unique user identifier \\ \hline
     SLA Param1&  FLOAT & SLA parameter placeholder\\ \hline
     SLA Param2&  FLOAT & SLA parameter placeholder\\ \hline
     SLA Param3&  FLOAT & SLA parameter placeholder\\ \hline
    \end{tabular}}
    \caption {Trace format description} \label{tab:format} 
\end{table}

@@

\begin{figure}[] 
\centering
\includegraphics[scale=0.25]{arrivalrate.png}
\caption{Arrival rate of jobs }
\label{fig:arrivalrate}
\end{figure}

@@

\begin{figure*}[]
\centering
\includegraphics[scale=0.65]{pie}
\caption{ Distribution of job count in various schedule classes}
 \label{fig:pie}
\end{figure*}

\begin{table*}
\adjustbox{max width=1\textwidth}{

\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|}
\hline
 & \multicolumn{3}{l|}{\bf{Trace A}} & \multicolumn{3}{l|}{\bf{Trace B}} & \multicolumn{3}{l|}{\bf{Trace C}} & \multicolumn{3}{l|}{\bf{Trace D}} & \multicolumn{3}{l|}{\bf{Trace E}} \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}Sched\\ Class\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg \\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ CPU\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Avg\\ Mem\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}RT\\  (secs)\end{tabular}} \\ \hline
0 & 0.075 & 0.051 & 415 & 0.123 & 0.096 & 345 & 0.083 & 0.065 & 385 & 0.093 & 0.092 & 373 & 0.093 & 0.074 & 333 \\ \hline
1 & 0.087 & 0.029 & 729 & 0.086 & 0.032 & 760 & 0.082 & 0.028 & 711 & 0.073 & 0.030 & 743 & 0.093 & 0.043 & 693 \\ \hline
2 & 0.067 & 0.043 & 1028 & 0.096 & 0.058 & 872 & 0.088 & 0.057 & 918 & 0.073 & 0.045 & 707 & 0.084 & 0.049 & 832 \\ \hline
3 & 0.088 & 0.12 & 1105 & 0.099 & 0.12 & 82 & 0.101 & 0.012 & 7961 & 0.081 & 0.051 & 17135 & 0.089 & 0.061 & 9021 \\ \hline
\end{tabular}
}
\caption {Trace set statistics} \label{tab:tracestat} 
\end{table*}

@@

\begin{figure}[] 
\centering
\includegraphics[scale=0.25]{runtime}
\caption{CDF of the job duration}
\label{fig:runtime}
\end{figure}

@@

\begin{figure} %
    \centering
    \subfloat[CPU resource ]{{\includegraphics[width=8cm]{cpu} }}%
    \newline

    \subfloat[RAM resource]{{\includegraphics[width=8cm]{mem} }}%
    \caption{CDF of resource requested by jobs}%
    \label{fig:resource}%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DATA CENTER PROFILING } \label{sec:datacenter}
In order to run our experiments, we need to collect information about data centers that will help us make better scheduling decisions. We call this process data center profiling. The major energy costs in data center are from running the IT resources and from cooling the data centers. We create a profile for each of the data center with the information that effects the energy costs.

\begin{table}[] 
 \centering
\begin{tabular}{|p{3cm}|l|p{2.5cm}|}
\hline
\bf{Location}                        & \bf{Label} & \bf{Associated Trace} \\ \hline
Berkeley County, South Carolina & DC1   & A                \\ \hline
Lenoir, North Carolina          & DC2   & B                \\ \hline
Singapore                       & DC3   & C                \\ \hline
Quilicura, Chile                & DC4   & D                \\ \hline
Dublin, Ireland                 & DC5   &   E               \\ \hline
\end{tabular}
\caption {Data center location information} \label{tab:dc}
\end{table}

@@

\begin{table}[] 
 \centering
\scalebox{0.8}{\begin{tabular}{|l|l|l|l|}
\hline
\bf{Node count}      &       \bf{Architecture}          & \bf{CPU} & \bf{Memory} \\ \hline
6732 & B & 0.5 & 0.50   \\ \hline
3863 & B & 0.5 & 0.25   \\ \hline
1001 & B & 0.5 & 0.75   \\ \hline
795 & C & 1 & 1   \\ \hline
126 & A & 0.25 & 0.25   \\ \hline
52 & B & 0.5 & 0.12  \\ \hline
5 & B & 0.5 & 0.3  \\ \hline
5 & B & 0.5 & 0.97  \\ \hline
3 & C & 1 & 0.50  \\ \hline
1 & B & 0.5 & 0.06  \\ \hline
\end{tabular}}
\caption {Data center IT resource configuration} \label{tab:dcres}
\end{table}

@@

\begin{figure*} %
    \centering
    \subfloat[Daily Average Temperature ]{{\includegraphics[width=8cm]{AverageTemp} }}%
    \subfloat[Daily Maximum Variation]{{\includegraphics[width=8cm]{Variation} }}%
    \caption{Temperature variation for the year 2013}%
    \label{fig:temp}%
\end{figure*}

@@

\section{SCHEDULER SIMULATOR} 
We plan to implement our simulator using CloudSim \cite{calheiros2011cloudsim}. CloudSim is an extensible simulation toolkit that enables modeling and simulation of Cloud computing systems and application provisioning environments. The CloudSim toolkit supports both system and behavior modeling of Cloud system components such as data centers, virtual machines (VMs) and resource provisioning policies.
\subsection{Components}
\begin{list2} %Job Description%
\item \textbf{Datacenter:} This component will simulate a data center. This composed of 1) scheduler that implements a specific provisioning algorithm, 2) data center profile database, 3) a work trace reader and 4)proxy elements of other data center for inter-data center communication\
\item \textbf{DataCenter Proxy}: All interactions with the data center will be through a proxy. Each datacenter will hold the proxies to other data centers.\
\item \textbf{Scheduler:} This component will implement the optimization technique and schedule jobs onto data centers.\
\item \textbf{Datacenter Profile DB}: This components contains the temperature and electricity data. Scheduler will access this to make provisioning decisions.\
\end{list2}

\begin{figure}[] 
\centering
\includegraphics[scale=0.40]{component}
\caption{Simulation components and their interaction}
\label{fig:component}
\end{figure}

@@

\section{CONCLUSION}
We have completed the work trace analysis and data center profiling parts of the project. Currently the simulator is being implemented, following which we will work on the energy minimization techniques and the final evaluation of these techniques. If time permits, we would also like to consider green energy in our provisioning mechanism. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\section{SCHEDULING ALGORITHM}

@@

{\footnotesize \bibliographystyle{acm}
\bibliography{sample}}
